Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-11-02 Supplemental-Material-A-Annotated-Analysis.Rmd
Update Supplemental-Material-A-Annotated-Analysis.Rmd

```{r variable names by response type}
varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(contactSpecific = recode(.$contactSpecific, 
                         `-1`="No Interaction Only",
                         `0`="unspecific",
                         `1`="Interaction Only")) %>%
  select(varNam, varGroup, contactSpecific) %>%
  group_by(varGroup, varNam, contactSpecific) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varGroup", "varNam"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("concept", "variable"), " - ") %>%
  arrange(concept, unspecific, `Interaction Only`) %>%
  mutate_all(~recode(.x, `0`="", ` 1`="✓")) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", rep("c", ncol(.)-2)),
      digits=2,
      caption = "Variables by Interaction Types") %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

@@

@@

@@

>>>>

```{r variable names by response type and study}
varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, varGroup, contactSpecific, study1, study2, study3) %>%
  group_by(varGroup, varNam, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varGroup", "varNam", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("concept", "variable", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  arrange(concept, unspecific, `Interaction Only`) %>% 
  mutate_all(~recode(.x, `0`="", ` 1`="✓")) %>%
  relocate(starts_with("study"), .after = last_col()) %>%
  rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", rep("c", ncol(.)-2)),
      digits=2,
      caption = "Variables by Interaction Types and Study Availability") %>%
  add_header_above(c(" " = 2, "Contact Type" = 2, "Study Availability" = 3)) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

@@

apply(dtS1Red, 2, sum(is.na(.))/nrow(.))

your_dataframe %>%
  group_by(Your_Participantid) %>%
  summarise(across(everything(), funs(100*mean(is.na(.)))))

@@

Feature selection types:

-   manual feature and variable selection
-   wrapper: procedures that add and/or remove predictors to find the optimal combination that maximizes model performance.
-   filter: relevance of the predictors outside of the predictive models and subsequently model only the predictors that pass some criterion.
-   dimension reduction for clustering. No selection more compression of redundant variance.

```{r manual feature selection}

```{r automated feature selection}

```{r dimension reduction}
raw_data <- featData
z_data <- featFullImp$featuresImpZ
scaled_data <- featFullImp$featuresImpZMat

res.pca <- prcomp(scaled_data, scale = FALSE)
fviz_eig(res.pca, addlabels = TRUE)

var <- get_pca_var(res.pca)
corrplot::corrplot(var$contrib[,1:10], is.corr=FALSE) 
fviz_contrib(res.pca, choice = "var", axes = 1, top = 50)
fviz_contrib(res.pca, choice = "var", axes = 2, top = 50)

res.desc <- FactoMineR::dimdesc(res.pca, axes = c(1,2), proba = 0.05)
# Description of dimension 1
res.desc$Dim.1

plot_ly(
  res.pca$rotation %>% as.data.frame,
  x = ~ PC1,
  y = ~ PC2,
  z = ~ PC3,
  size = 2,
  type = 'scatter3d',
  mode = 'markers',
  text = ~ paste('Variable:', rownames(res.pca$rotation))
) %>%
  layout(title = 'Variables in reduced space')
plot_ly(
  res.pca$x %>% as.data.frame,
  x = ~ PC1,
  y = ~ PC2,
  z = ~ PC3,
  size = 2,
  type = 'scatter3d',
  mode = 'markers',
  text = ~ paste('Participant:', rownames(res.pca$x))
) %>%
  layout(title = 'Participants in reduced space')

pca.out <- as.data.frame(res.pca$x[,1:3])

# load libraries
library(factoextra)
library(NbClust)
# elbow method
fviz_nbclust(pca.out, kmeans, method = "wss") +
  geom_vline(xintercept = 2, linetype = 2)+
  labs(subtitle = "Elbow method")
# Silhouette method
fviz_nbclust(pca.out, kmeans, method = "silhouette")+
  labs(subtitle = "Silhouette method")
# Gap statistic [takes for ever]
# nboot = 50 to keep the function speedy.
# recommended value: nboot= 500 for your analysis.
# Use verbose = FALSE to hide computing progression.
# set.seed(123)
# fviz_nbclust(scaled_data, kmeans, nstart = 100,  method = "gap_stat", nboot = 500)+
#   labs(subtitle = "Gap statistic method")

kmeansOut <- kmeans(pca.out, centers = 3, nstart = 100)
fviz_cluster(kmeansOut, geom = "point", data = scaled_data, ggtheme = theme_Publication())

# MCLUST
library(mclust)
BIC <- mclustBIC(pca.out)
plot(BIC)
summary(BIC)
mod1 <- Mclust(pca.out)
summary(mod1, parameters = FALSE)

# DBSCAN
library(dbscan)
library(fpc)

# to plot the eps values
eps_plot = kNNdistplot(pca.out, k=3)
# to draw an optimum line
eps_plot %>% abline(h = 3.5, lty = 2)

potentialMinPts <- round(SciViews::ln(nrow(pca.out)))
eps <- 3.5
minPts <- 2

fviz_cluster(res.fpc, scaled_data, geom = "point", ggtheme = theme_Publication())

@@

```{r time-series linear trends by variable and cluster}
data.frame(ID = as.numeric(names(kmeansOut$cluster)), cluster = kmeansOut$cluster) %>%
  merge(., raw_data) %>%
  select(
    ID,
    TIDnum,
    cluster,
    any_of(varNamS123)
  ) %>%
  reshape2::melt(id.vars = c("cluster", "ID","TIDnum")) %>% 
  ggplot(., aes(x=TIDnum, y=value, group=cluster, color=as.factor(cluster))) +
  geom_line(aes(x=TIDnum, y=value, group=ID, color=as.factor(cluster)), alpha=0.05) +
  geom_smooth(aes(group=cluster)) +
  #stat_summary(fun=mean, geom="line") +
  facet_wrap(~ variable, scales = "free_y") +
  labs(
    x = "Time ID",
    y = "Response (Mean Cluster Response Bold)",
    color = "Cluster"
  ) +
  theme_Publication()
```
